---
title: "Assignment 4"
author: "Edy Kim"
date: "10/24/2020"
output: github_document
---

```{r, message = FALSE}
library(parallel)
library(tidyverse)
library(microbenchmark)
```

# HPC 

## Problem 1: Make Sure Your Code is Nice 

```{r}
# Total row sums
fun1 <- function(mat) {
  n <- nrow(mat)
  ans <- double(n)
  for (i in 1:n) {
    ans[i] <- sum(mat[i, ])
  }
  ans
}

fun1alt <- function(mat) {
  rowSums(mat)
}

# Cumulative sum by row
fun2 <- function(mat) {
  n <- nrow(mat)
  k <- ncol(mat)
  ans <- mat
  for (i in 1:n) {
    for (j in 2:k) {
      ans[i,j] <- mat[i, j] + ans[i, j - 1]
    }
  }
  ans
}


fun2alt <- function(mat) {
  t(apply(dat,1,cumsum))
}

# Use the data with this code
set.seed(2315)
dat <- matrix(rnorm(200 * 100), nrow = 200)

# Test for the first
microbenchmark::microbenchmark(
  fun1(dat),
  fun1alt(dat), unit = "relative", check = "equivalent")

# Test for the second
microbenchmark::microbenchmark(
  fun2(dat),
  fun2alt(dat), unit = "relative", check = "equivalent"
)

```

After fun1 was altered to be more efficient, it was determined that the alternate fun1alt was overall faster in processing than the original function. On average, the fun1alt function was around 5.6941 times faster than the original fun1 function. 

After fun2 was altered to be more efficient, it was determined that the alternate fun2alt was overall faster in processing than the origina function. On average, the fun2alt function was around 3.296 times faster than the original fun2 function. 


```{r}
sim_pi <- function(n = 1000, i = NULL) {
  p <- matrix(runif(n*2), ncol = 2)
  mean(rowSums(p^2) < 1) * 4
}

# Here is an example of the run
set.seed(156)
sim_pi(1000) # 3.132

# This runs the simulation a 4,000 times, each with 10,000 points
set.seed(1231)
system.time({
  ans <- unlist(lapply(1:4000, sim_pi, n = 10000))
  print(mean(ans))
})
```

# SQL

```{r}
# install.packages(c("RSQLite", "DBI"))

library(RSQLite)
library(DBI)

# Initialize a temporary in memory database
con <- dbConnect(SQLite(), ":memory:")

# Download tables
film <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film.csv")
film_category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film_category.csv")
category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/category.csv")

# Copy data.frames to database
dbWriteTable(con, "film", film)
dbWriteTable(con, "film_category", film_category)
dbWriteTable(con, "category", category)


```

```{sql, connection=con}
PRAGMA table_info(film)
```

```{sql, connection=con}
PRAGMA table_info(film_category)
```
```{sql, connection=con}
PRAGMA table_info(category)
```

## Question 1: How many movies is there available in each rating category?

```{sql, connection=con}
SELECT rating,
COUNT(*) AS count
FROM film
GROUP BY rating
```

## Question 2: What is the average replacement cost and rental rate for each rating category? 

```{sql, connection = con}
SELECT rating,
  AVG(replacement_cost) AS avg_replacement_cost,
  AVG(rental_rate) AS avg_rental_rate
FROM film 
GROUP BY rating
```

## Question 3: Use table film_category together with film to find how many films there are with each category ID

```{sql, connection = con}
SELECT c.category_id,
  COUNT(*) AS count
FROM film AS f
  INNER JOIN film_category AS c
ON f.film_id = c.film_id
GROUP BY category_id
```

## Question 4: Incorporate table category into the answer to the previous question to find the name of the most popular category 

```{sql, connection = con}
SELECT c.category_id,name,
  COUNT(*) AS count
FROM film AS f
  INNER JOIN film_category AS c ON f.film_id = c.film_id
  JOIN category AS r ON c.category_id = r.category_id
GROUP BY c.category_id
ORDER BY count DESC
```

The name of the most popular movie categories were ordered by popularity. The most popular category is sports, with a count of 74, while the least popular is music, with a count of 51. 